---
title: "The Impact of Mobile Phone Features on Pricing: A Statistical Approach"
author: "Ang Jia Yi"
date: "2024-07-10"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: true
    theme: cerulean
editor_options:
  markdown:
    wrap: 72

---

```{=html}
<style>
p {
    text-align: justify;
}
</style>
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

packages <- c('diagram','matlib','optimbase', 'tidyverse','readr','ggplot2','dplyr','ggcorrplot','MASS','olsrr','AICcmodavg','leaps','caTools','car','corrplot','summarytools','gridExtra') 
new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

lapply(packages, require, character.only = TRUE)

```

# Topic Overview

In the rapidly evolving mobile phone market, it is crucial for companies
to develop competitive and well-priced products to capture different
market segments. It is found that the mobile phone price and product
features will influence the consumers’ purchasing intention. Geçit and
Kayacan (2017) found that mobile phone price has a negative effect on
the consumers’ mobile phone purchase decision, which as the price
increases, the intention of consumers to purchase the mobile phone
decreases. Besides, Manandhar and Timilsina (2023) stated that the
mobile phone features significantly impact the purchasing decisions of
consumers, where they further suggested mobile phones companies to
conduct market research to determine the features demanded by the
consumers such as camera resolution, a stylish and lighter design, or
any innovative software and hardware advancement to boost sales.
However, the pricing of a mobile phone is also often influenced by the
features it possesses. Hence, a balance is needed to be achieved between
the features associated with a mobile phone and its price, so that
consumers have higher intention to purchase it.

To achieve this, predictive modelling can be a valuable tool. By
analysing historical data on mobile phone features and their
corresponding prices, we can identify which variables most significantly
influence pricing. This analysis will help us establish an effective
pricing model that optimally reflects the attributes of each market
segment. Key features to consider include weight, thickness, battery
capacity, screen size, pixels per inch (PPI), rear camera, front camera,
number of CPU cores, CPU frequency, internal memory, and RAM.

The objective of this project is to develop predictive models using
various combinations of these features to determine the optimal set of
variables that best predict mobile phone prices. The insights gained
will guide the pricing strategy for the new mobile phone series,
ensuring that each model is competitively priced and aligned with market
expectations.

<br>

# Problem

## Scenario

As the head of the product development team at a leading mobile phone
company, you are tasked with launching a new series of mobile phones.
This series will include models targeting different market segments:
budget, mid-range, and premium. After some research, it is found that
apart from mobile phone price, the product features will also influence
the purchasing decision of consumers (Geçit & Kayacan, 2017; Manandhar &
Timilsina, 2023). Therefore, to optimize the pricing strategy, you need
to consider various factors that influence the cost and perceived value
of the mobile phones. These factors include weight, thickness, battery
capacity, screen size, pixels per inch (PPI), rear camera, front camera,
number of CPU cores, CPU frequency, internal memory, and RAM.

## Problem Statement

Develop predictive models using various combinations of features
(including weight, thickness, battery capacity, screen size, camera
specifications, CPU performance, internal memory, and RAM) to identify
which variables have the most significant influence on mobile phone
pricing. The objective is to determine the optimal combination of
features that best predicts prices and to establish the most effective
pricing model for the new mobile phone series across budget, mid-range,
and premium segments.

<br>

# Data

The dataset used for this analysis is a mobile price prediction dataset,
sourced from Kaggle (Younesi, 2022). This dataset includes a
comprehensive set of features related to mobile phone specifications and
their corresponding prices. The mobile phone specifications include
weight, thickness, battery capacity, screen resolution, PPI, rear
camera, front camera, CPU cores, CPU frequency, internal memory, and
RAM. This makes the dataset an ideal resource for developing predictive
pricing models. The variable “Sale” has been excluded during data
extraction, as we are investigating the impact of mobile phone features
on its price.

During the initial data extraction, we encountered a variable labeled
"type of CPU cores" However, the data for this variable consisted of
numerical values ranging from 0 to 8. Upon closer examination, it became
evident that these numbers more accurately represented the number of CPU
cores in each mobile phone rather than different types of CPU cores.

To ensure the integrity and usability of our dataset, we decided to
treat this variable as representing the number of CPU cores.
Consequently, the variable was renamed to "number of CPU cores" to
reflect its true nature. Additionally, any entries with a value of 0 for
the number of CPU cores were treated as missing data. These entries were
subsequently removed from the dataset to avoid any inaccuracies or
potential biases in our analysis. This preprocessing step was crucial to
ensure that the dataset accurately represents the specifications of the
mobile phones under study.

Furthermore, during our analysis on the data found, we found that the
data for the resolution is represented by a single number. For example,
4, 4.7 and 5.5, which is actually describing the screen size of the
mobile phone in inches rather than the the resolution of the mobile
phone, which should be represented by two numbers, for example, 1920 x
1080 pixels and 2560 x 1440 pixels. Hence, we decide to amend the
variable name from resolution to screen size.

## Data Description

### Weight

Weight is the total mass of a mobile phone, which is significant for
comfort and long-term usage, with a balance between durability and
convenience. The weight often correlates with other factors that
contribute to a mobile phone's cost. For instance, research indicates
that features like a larger battery or more robust materials, which
contribute to a phone's weight, can also increase its price due to their
added value and production costs​ (Mustafa & Al-Rifat, 2019). Hence, the
new mobile phones’ features should be built within a certain weight that
does not burden the daily usage of consumers. This could potentially
influence the production costs and the final price of the mobile phones
launched.

### Thickness

The thickness of a mobile phone can determine whether its appearance is
aesthetically and in line with consumers’ perception. Octaviani and
Rahmawan (2023) found that customer buying interest in iPhone Mini is
positively and significantly influenced by product design. However,
usually the mobile phone price increases as its thickness decreases.
This is due the increase in production costs as it requires more
advanced engineering and design to maintain the phone performance and
durability while minimising bulk. The research made by Elsheikh et al.
(2023) has highlighted that the effort to balance thinness with
functionality and battery life necessitates costlier, compact components
and materials, leading to higher prices​. Hence, an optimal thickness of
the mobile phone is needed to balance between its price and performance.

### Battery

Mobile phone batteries with higher capacity will have longer battery
life, which is a driving factor of higher mobile phone price. Negi and
Pandey (2013) discovered that the longest battery backup is the most
important consideration for young females in Bangladesh when purchasing
mobile phones. Besides, batteries with advanced technology features such
as fast charging and wireless charging are also more costly. Shalahb
Gaur (2019) found that wireless charging technology that is energy
conversion efficient is costlier. Hence, a battery with better quality
can increase the phone’s performance and longevity, contributing to
higher costs. Therefore, the battery brand and technology used would
also influence the price of the new mobile phones.

### CPU Frequency (CPU_freq)

CPU frequency, measured in gigahertz (GHz), significantly impacts the
speed at which a device processes data. Higher clock speeds mean that
the processor can execute tasks more rapidly, enhancing everything from
simple phone functions to complex application performance. Intel (n.d.)
notes that within the same CPU generation, processors with greater clock
speeds usually perform better than those with lower speeds in various
tasks. As a result, mobile phones with higher CPU frequencies often
deliver superior performance, which typically leads to higher market
prices.

### Internal memory (InternalMem)

Internal memory is a key factor in enhancing a mobile phone's usability.
With more internal storage, a device can accommodate more applications
and store greater amounts of data, which helps maintain the phone's
performance over time. As a result, mobile phones with larger storage
capacities are perceived as more versatile and powerful, justifying
higher price tags. This is particularly relevant as the size
requirements for media files and apps grow. For instance, the base model
of the iPhone 13 with 128GB is priced at \$799, but upgrading to 256GB
costs an additional \$100, while a jump to 512GB adds another \$400 to
the price. Thus, fully upgrading the storage capacity can nearly double
the cost of the iPhone 13 (Bowe, 2021). Clearly, internal storage is not
just a component—it's a significant investment that reflects and
enhances a mobile phone's market value.

### RAM

RAM (Random Access Memory) is a crucial element influencing mobile phone
pricing. Increased RAM capacity enables smoother operation of multiple
apps at once, essential for high-end gaming and professional
applications that demand significant memory. As a result, phones with
greater RAM can handle more tasks efficiently, leading to higher pricing
due to improved multitasking performance and speed. While the presence
of more RAM does raise the manufacturing cost of a mobile phone, it is
considered a standard component. However, it's important to note that
other hardware components often play a more direct role in determining
the final price of the phone (ScientiaMobile, 2022).

### Number of CPU cores (CPU_core)

The number of CPU cores is a pivotal factor in determining the
multitasking capabilities and overall performance of a mobile phone.
Having more cores allows a phone to process multiple tasks
simultaneously, enhancing performance in applications that require
multi-threading and improving overall efficiency in power usage.
Essentially, the number of cores in a CPU signifies the device's ability
to handle concurrent tasks; thus, phones equipped with more cores
typically offer superior multitasking capabilities (Lebara, 2024). This
increased capacity for multitasking not only boosts the phone's
usability and responsiveness but also contributes to higher energy
efficiency. As a result, mobile phones with greater core counts command
higher prices in the market due to their enhanced performance and
advanced capabilities.

### Screen Size (ScreenSize)

The screen size of a mobile phone is measured across the screen, from
one corner to the opposite corner, and defined in inches. It is
important for business users who frequently need to view two apps at
once on their phone while multitasking with the multiple window feature
(Arnold, 2017). The screen size will affect the cost of producing a
mobile phone (Pakalka & Noreika, n.d.). The higher cost will lead to a
higher price. Thus, the screen size is the factor that affects the final
price of a mobile phone.

### Pixels Per Inch (PPI)

Pixels per inch (PPI) is calculated by dividing the diagonal resolution
of the screen (in pixels) by the diagonal size of the screen (in
inches). The screen of a mobile phone with a higher PPI will display
images that are sharper and more detailed. However, it will cost more
and require longer battery life for a mobile phone’s screen with a
higher PPI (FasterCapital, 2024). Hence, PPI will affect the final price
of a mobile phone.

### Rear Camera (RearCam)

Mobile phone technology has advanced far more quickly than that of most
"proper" cameras because of the substantially larger research and
development expenditures that are made by technology companies like
Samsung and Apple (Dawood, 2018). Hence, with the larger capital
invested in R&D to develop the rear camera, the price of the mobile
phone will increase along with the development of the camera, and it
also implies that the development of the number of Megapixels (MP)
(resolution of a digital image or camera sensor) of the mobile phone
will influence the final price of the mobile phone.

### Front Camera (FrontCam)

The primary uses of the front camera are "selfies", facial recognition
and iris scanning for devices (Everphone, n.d.). According to NEC
(2022), the iPhone 13 was the most expensive mobile phone in 2022 due to
Apple's introduction of facial recognition technology. The front camera
with higher Megapixels (MP) will indirectly improve face recognition
performance. Hence, the improvement in the MP of the front camera will
affect the price of the mobile phone.

<br>

# Extract and Examine the data

```{r}

# Read dataset
data_phone <- read.csv("C:/Users/User/Desktop/SUNWAY/Y3S2 REGRESSION ANALYSIS/Cellphone.csv", header=TRUE)

# Look at the structure of the variables
str(data_phone)

# View the summary of the dataset
summary(data_phone)

price <- data_phone$Price
variables <- names(data_phone)[-1]  # Excluding the "Price" column

# Set up the plotting area
par(mfrow = c(3, 4))  # Adjust the number of rows and columns as needed

# Loop through each variable and plot against Price
for (variable in variables) {
  plot(price, data_phone[[variable]], main = paste("Price vs", variable),
       xlab = "Price", ylab = variable)
}

# Reset the plotting area to default
par(mfrow = c(1, 1))

```

## Scatter plot analysis

-   **Price vs Screen Size and Price vs Weight:** There is no
    discernible trend, suggesting that the weight of a phone and the
    screen size does not have a significant impact on its price.

-   **Price vs PPI:** The plot displays a positive trend, indicating
    that higher pixel density could contribute to higher prices,
    reflecting consumer preferences for better display quality.

-   **Price vs CPU Core and Price vs CPU Frequency:** The plots show
    that higher numbers of CPU cores and higher CPU frequencies tend to
    be associated with higher-priced phones, emphasizing the value
    placed on processing power.

-   **Price vs Internal Memory and Price vs RAM:** Both attributes show
    a positive relationship with price, which means phones with more
    memory and RAM are generally priced higher, likely due to better
    performance capabilities.

-   **Price vs Rear Camera and Price vs Front Camera:** The plots show
    some level of positive relationship, especially with higher
    specifications of rear cameras, suggesting that better camera
    quality may influence the price, though the relationship is not as
    strong as it is with internal memory or CPU specs.

-   **Price vs Battery:** There's a slight positive relationship,
    indicating that phones with larger battery capacities tend to have
    higher prices, likely due to the longer usage they offer.

-   **Price vs Thickness:** This plot reveals a moderate negative trend,
    suggesting a possible consumer preference for thinner devices, which
    might be associated with higher prices.

The scatter plots collectively examine the relationship between various
technical specifications of mobile phones and their market prices.
Generally, performance-related specifications such as **CPU frequency,
internal memory, and RAM** show a clear positive correlation with price,
suggesting that higher performance metrics are associated with
higher-priced models, reflecting consumer demand for more powerful
devices. Similarly, features that enhance user experience, namely
**battery capacity**, also tend to increase with price, indicating a
market preference for longer battery life. Interestingly, **camera
specifications, both rear and front**, show a more moderate impact on
pricing, suggesting that while important, they may not be the primary
driver of price differences. Conversely, the **thickness** of phones
shows a moderate negative relationship with price, hinting at a premium
on sleeker, thinner designs. Overall, these plots underscore the
multifaceted factors that contribute to the pricing of mobile devices,
with a strong emphasis on performance and user experience enhancements.

<br>

# Correlation Matrix

```{r}

# Calculate the correlation matrix for the data_phone dataset and round the values to 4 decimal places
rounded_correlation_matrix <- round(cor(data_phone), 4)
rounded_correlation_matrix

# Plot the correlation matrix using the corrplot package, displaying only the lower triangular part of the matrix
corrplot::corrplot(rounded_correlation_matrix, type = 'lower')

```

## Interpretation

**Very Strong Positive Correlation:**

-   **RAM and Price (0.8922):** A very strong positive correlation
    exists between RAM and price, demonstrating that higher RAM
    significantly increases mobile phone prices. This correlation is the
    strongest among all the predictors, indicating RAM as a crucial
    pricing factor.

**Strong Positive Correlation:**

-   **Internal Memory and Price (0.7920):** A strong positive
    correlation suggests that mobile phones with larger internal memory
    command higher prices, emphasizing the importance of storage
    capacity in price determination.
-   **PPI and Price (0.7877):** A strong positive correlation indicates
    that higher PPI, enhancing screen sharpness, tends to increase the
    mobile phone's price significantly.
-   **Rear Camera and Price (0.6787):** A strong positive correlation
    between rear camera quality and price reflects consumer demand for
    high-quality photography capabilities.
-   **Front Camera and Price (0.6500):** Strong positive correlation
    shows that superior front camera quality, crucial for selfies and
    video calls, can drive up mobile phone prices.

**Moderate Positive Correlation:**

-   **CPU Frequency and Price (0.6079):** Higher CPU frequencies,
    enhancing processing speed, correlate moderately with higher mobile
    phone prices.
-   **CPU Core and Price (0.5770):** The number of CPU cores, which
    facilitates multitasking, shows a moderate positive correlation with
    price.
-   **Battery and Price (0.4679):** Larger battery capacities, offering
    extended usage, are moderately associated with higher prices.

**Weak Positive Correlation:**

-   **Screen Size and Price (0.1850):** A weak positive correlation
    indicates that larger screen sizes may slightly influence the price,
    though they are not a primary price determinant.

**Very Weak Positive Correlation**

-   **Weight and Price (0.0338):** A negligible positive correlation
    suggests that weight has minimal impact on the price of mobile
    phones.

**Negative Correlation:**

-   **Thickness and Price (-0.6194):** A strong negative correlation
    shows that thinner mobile phones are generally more expensive,
    reflecting the higher costs associated with their design and
    production.

<br>

# Fit the model

## Full Model

```{r}

# Fit a linear regression model to predict Price using all variables in data_phone
full_model <- lm(Price ~ ., data = data_phone)

# Display a summary of the full_model
summary(full_model)

```

**Model Performance:**

-   **Residual standard error:** 173.7 on 139 degrees of freedom
-   **Multiple R-squared:** 0.9401
    -   Indicates that 94.01% of the variance in price is explained by
        the model.
-   **Adjusted R-squared:** 0.9354
    -   Adjusted for the number of predictors, still indicating a very
        good fit.
-   **F-statistic:** 198.5 on 11 and 139 DF, p \< 2.2e-16
    -   Overall model is highly significant.

**Significance Summary:**

We can observe the significance of each coefficients from the summary
above:

-   **Significant Positive Predictors:** PPI, CPU Core, CPU Frequency,
    Internal Memory, RAM, Battery
-   **Significant Negative Predictors:** Screen Size, Thickness
-   **Non-significant Predictors:** Weight, Rear Camera, Front Camera

These results suggest that higher PPI, more CPU cores, higher CPU
frequency, more internal memory, more RAM, and larger battery capacity
are associated with higher mobile phone prices. In contrast, larger
screen size and greater thickness are associated with lower prices.
Weight, rear camera, and front camera do not have significant effects on
the price.

**Conclusion:**

The analysis demonstrates that multiple factors, including PPI, CPU core
count, CPU frequency, internal memory, RAM, and battery capacity,
strongly influence mobile phone prices. The significant F-statistic and
a high R-squared value (0.9401) confirm that these predictors
collectively offer a reliable basis for forecasting mobile phone prices.
This model effectively explains 94.01% of the variability in price,
underscoring the importance of processing power, memory capacity, and
battery life in determining phone costs. However, to account for the
remaining 6% of variability in price, further analysis might explore
additional variables or external market factors.

<br>

## Fit some smaller models

### Model 1

This model investigates the relationship between the Price of a mobile
phone and its RAM.

```{r}

# Fit a linear regression model to predict Price using RAM as the predictor
model1 <- lm(Price ~ RAM, data = data_phone)

# Display a summary of the model1
summary(model1)

```

**Coefficients:**

-   **Intercept (1396.61):** This is the estimated price when RAM is
    zero, highly significant (p \< 0.001). This value is the baseline
    price without considering the RAM effect.
-   **RAM (391.24):** This coefficient represents the expected change in
    price for each additional unit of RAM. It indicates a highly
    significant (p \< 0.001) positive relationship between RAM and
    price. Specifically, for each 1 GB increase in RAM, the price is
    expected to increase by approximately 391.24 units.

**Model Performance:**

-   **Residual standard error:** 309.8 on 149 degrees of freedom
    -   This error term indicates the average difference between the
        observed values and the model's predictions, suggesting moderate
        variability around the predicted values.
-   **Multiple R-squared:** 0.796
    -   This statistic means that approximately 79.6% of the variability
        in mobile phone price is explained by the RAM alone, which is a
        strong fit for such a simple model.
-   **Adjusted R-squared:** 0.7946
    -   Adjusting for the number of predictors, the model still explains
        roughly 79.46% of the variance, reinforcing the effectiveness of
        RAM in predicting price.
-   **F-statistic:** 581.4 on 1 and 149 degrees of freedom, with a
    p-value \< 2.2e-16
    -   This highly significant F-statistic indicates that the model is
        statistically significant, meaning RAM is a crucial predictor of
        mobile phone price.

**Conclusion:**

The analysis shows a strong positive relationship between the amount of
RAM in a mobile phone and its price. The significant F-statistic and
high R-squared value confirm that RAM is an excellent predictor of price
in this dataset. This model is reliable for predicting mobile phone
prices based on RAM but may benefit from considering other variables to
account for the remaining 20% of variability in price.

<br>

### Model 2

This model investigates the relationship between the price of a mobile
phone and its thickness.

```{r}

# Fit a linear regression model to predict Price using Thickness as the predictor
model2 <- lm(Price ~ Thickness, data = data_phone)

# Display a summary of model2
summary(model2)

```

**Coefficients:**

-   **Intercept (4633.25):** This is the estimated price when thickness
    is zero, highly significant (p \< 0.001). This value serves as the
    baseline price assuming the absence of the thickness variable.
-   **Thickness (-271.43):** This coefficient represents the expected
    change in price for each one-unit increase in thickness. The
    negative value (-271.43) is highly significant (p \< 0.001),
    indicating that an increase in thickness tends to decrease the
    mobile phone's price. This matches the intuitive notion that sleeker
    (thinner) phones might be priced higher due to consumer preferences
    or manufacturing costs.

**Model Performance:**

-   **Residual standard error:** 538.4 on 149 degrees of freedom
    -   This error term reflects the average deviation of the observed
        prices from the predicted values, indicating a somewhat high
        variability.
-   **Multiple R-squared:** 0.3836
    -   This value suggests that approximately 38.36% of the variability
        in mobile phone price is explained by the thickness alone. This
        indicates a moderate explanatory power of the model.
-   **Adjusted R-squared:** 0.3795
    -   This adjusted metric accounts for the number of predictors (one
        in this case) and suggests a similar explanatory power after
        adjustment.
-   **F-statistic:** 92.73 on 1 and 149 degrees of freedom, with a
    p-value \< 2.2e-16
    -   The highly significant F-statistic confirms that the model is
        statistically significant, indicating that thickness is a
        crucial factor affecting the price of mobile phones, albeit not
        the only one given the R-squared value.

**Conclusion:**

The analysis shows a strong negative relationship between the thickness
of a mobile phone and its price, with thinner phones generally
commanding higher prices. While the model's fit is moderate, indicating
that other factors also play significant roles in pricing, thickness
alone has a clear and statistically significant impact on price.

<br>

### Model 3

This model includes both RAM and thickness as predictors for Price.

```{r}

# Fit a linear regression model to predict Price using RAM and Thickness as predictors
model3 <- lm(Price ~ RAM + Thickness, data = data_phone)

# Display a summary of model3
summary(model3)

```

**Coefficients:**

-   **Intercept (2567.08):** This is the baseline price when both RAM
    and thickness are zero. It is highly significant (p \< 0.001),
    suggesting a strong baseline influence on price.
-   **RAM (337.08):** The coefficient for RAM is highly significant (p
    \< 0.001) and positive, indicating that each unit increase in RAM
    (likely measured in GB) is associated with an increase in price by
    about 337.08 units. This result corroborates the known influence of
    RAM on enhancing device performance and consequently its price.
-   **Thickness (-122.17):** The coefficient for thickness is also
    highly significant (p \< 0.001) but negative, indicating that each
    unit increase in thickness is associated with a decrease in price by
    about 122.17 units. This may reflect market preferences for thinner
    devices, which are often considered more modern and portable.

**Model Performance:**

-   **Residual standard error:** 258.9 on 148 degrees of freedom
    -   Indicates the average deviation of the observed prices from
        those predicted by the model, suggesting moderate variability
        around the predicted values.
-   **Multiple R-squared:** 0.8585
    -   This statistic means that approximately 85.85% of the
        variability in mobile phone price is explained by the model,
        which is quite high, indicating a strong fit.
-   **Adjusted R-squared:** 0.8566
    -   Adjusting for the number of predictors (two in this case), the
        model still explains about 85.66% of the variance, reinforcing
        the effectiveness of RAM and thickness in predicting price.
-   **F-statistic:** 448.8 on 2 and 148 degrees of freedom, with a
    p-value \< 2.2e-16
    -   This highly significant F-statistic indicates that the model
        overall is statistically significant, meaning both RAM and
        thickness are crucial predictors of mobile phone price.

**Conclusion:**

Model 3 demonstrates a strong ability to predict mobile phone prices
based on RAM and thickness. The positive effect of RAM and the negative
effect of thickness are both statistically significant and substantial.
The high R-squared values suggest that including these two predictors
provides a robust model for explaining price variability, although some
outliers and extreme values indicate potential limits to the model's
applicability across all observations.

<br>

## Calculate VIF

VIF measures how much the variance of a regression coefficient is
inflated due to multicollinearity with other predictors in the model. -
**VIF = 1:** No multicollinearity (each predictor is not correlated with
others). - **1 \< VIF \< 5:** Moderate multicollinearity (acceptable
levels). - **VIF \> 5:** High multicollinearity (problematic, requires
attention). - **VIF \> 10:** Very high multicollinearity (often
considered unacceptable)

```{r}

# Calculate VIF values for the full_model
vif_values <- vif(full_model)

# Create a horizontal bar plot of VIF values
barplot(vif_values, main = "VIF Values", horiz = TRUE, col = "steelblue", las = 1, cex.names = 0.6)

# Add a vertical dashed line at VIF = 5
abline(v = 5, lwd = 3, lty = 2)

```

**Summary**

-   **High Multicollinearity:**
    -   **Weight** and **Screen Size** exhibit very high VIF values,
        which could seriously affect the reliability of the regression
        coefficients associated with these predictors.
-   **Moderate Multicollinearity:**
    -   **Battery, RAM**, and **Internal Memory** are above the VIF
        threshold of 5, suggesting these factors also contribute to
        multicollinearity, albeit not as severely as Weight and
        Resolution.
-   **Low Multicollinearity:**
    -   **Thickness, Front Camera, Rear Camera, CPU Frequency, CPU
        Core**, and **PPI** have VIF values below 5, indicating that
        multicollinearity is less of a concern for these variables.

<br>

### Model 4

From the VIF results above, we can thus derive a model.This model
predicts price using all other variables in the dataset except for
battery, RAM, internal memory, screen size, and weight due to their high
VIF values.

```{r}

# Fit a linear regression model to predict Price according to the VIF approach
model4 <- lm(Price ~ . -Battery -RAM -InternalMem -ScreenSize -Weight, data = data_phone)

# Display a summary of model4
summary(model4)

```

**Model Performance:**

-   **Residual Standard Error:** 304.2 on 144 degrees of freedom
    -   Reflects the average size of the residuals.
-   **Multiple R-squared:** 0.8098
    -   Approximately 80.98% of the variability in phone price is
        explained by the model, which is quite high.
-   **Adjusted R-squared:** 0.8019
    -   Adjusts the R-squared for the number of predictors used, still
        indicating a strong model.
-   **F-statistic:** 102.2 on 6 and 144 DF, with a p-value \< 2.2e-16
    -   The model is statistically significant, meaning the predictors
        collectively influence the phone price significantly.

**Significance Summary:**

We can observe the significance of each coefficients from the summary
above:

-   **Significant Positive Predictors:** PPI, CPU Core, CPU Frequency,
    Front Camera
-   **Significant Negative Predictors:** Thickness
-   **Non-significant Predictors:** Rear Camera

**Conclusion:**

This model effectively explains a substantial portion of the variability
in phone prices based on several key features, despite excluding
variables prone to multicollinearity. The significant predictors like
PPI, CPU frequency, front camera, and thickness have clear associations
with price, confirming their importance in determining mobile phone
pricing. The model's overall fit is robust, but careful attention might
be needed for potential outliers or unusual data points suggested by the
spread in residuals.

<br>

## Best Subset Selection using BIC

Best subset selection using BIC evaluates all possible combinations of
predictors and selects the model that minimises the Bayesian Information
Criterion (BIC), balancing fit and complexity. BIC penalises the
inclusion of additional predictors to avoid overfitting, ensuring the
selected model is both accurate and interpretable. This method
identifies the most significant predictors, optimising the model's
explanatory power while maintaining simplicity.

```{r}

# Perform subset selection with up to 12 predictors and 2 best models for each subset size
subset_model <- regsubsets(Price ~ ., data = data_phone, nbest = 2, nvmax = 12)

# Display a summary of the subset selection results
summary(subset_model)

# Plot the results of the subset selection
plot(subset_model)

```

**From the Chart:**

-   **Shades of Gray:** The shades of gray indicate the BIC values, with
    darker shades representing lower (better) BIC values. Lighter shades
    represent higher BIC values, suggesting less optimal models
    according to the criterion.
-   **Predictor Inclusion:** Each filled block in the chart indicates
    that the predictor (column) is included in the model (row). The
    absence of a block means the predictor is not included in that
    particular model.

The best subset selection chart using BIC provides a visual
representation of the most effective combinations of predictors for
different model sizes. By examining the chart, we can identify that the
optimal model includes the predictors: PPI, CPU_core, CPU_freq,
InternalMem, Ram, ScreenSize, Battery, and Thickness. This optimal model
is indicated by the row with the lowest BIC value, suggesting it offers
the best balance between model fit and complexity. Predictors like PPI
and CPU_core appear consistently in the best models across different
sizes, highlighting their significant role in predicting the price of
mobile phones. The chart demonstrates that while adding more predictors
generally improves the model up to a point, including too many
predictors can lead to overfitting, as indicated by increasing BIC
values. Therefore, the identified optimal model provides robust and
interpretable predictions, balancing the need for accuracy with the
simplicity of the model.

<br>

### Model 5

From the BIC results above, we can thus derive a model. This model
predicts the price based on all available variables except for weight,
rear camera, and front camera. These variables were likely excluded
based on previous BIC results to optimise the model.

```{r}

# Fit a linear regression model to predict Price according to the results of the BIC approach
model5 <- lm(Price ~ . -Weight -RearCam -FrontCam, data = data_phone)

# Display a summary of model5
summary(model5)

```

**Model Performance:**

-   **Residual standard error:** 173.7 on 142 degrees of freedom
    -   Indicates variability around the fitted values, with a
        reasonably low error suggesting good model fit.
-   **Multiple R-squared:** 0.9388
    -   About 93.88% of the variability in phone prices is explained by
        this model, which is very high, showing excellent explanatory
        power.
-   **Adjusted R-squared:** 0.9354
    -   Adjusts the R-squared for the number of predictors, still
        indicating a strong fit.
-   **F-statistic:** 272.5 on 8 and 142 DF, p-value: \< 2.2e-16
    -   The overall model fit is statistically significant, suggesting
        that the predictors collectively have a significant effect on
        phone prices.

**Significance Summary:**

We can observe the significance of each coefficients from the summary
above:

-   **Significant Positive Predictors:** PPI, CPU Core, CPU Frequency,
    Internal Memory, RAM, Battery
-   **Significant Negative Predictors:** Screen Size, Thickness

**Conclusion:**

Model 5 effectively captures the relationship between various phone
characteristics and their prices with a high degree of explanatory
power. Key performance specifications like PPI, CPU specifications, RAM,
and design aspects like thickness are significant drivers of price. This
model, streamlined by BIC selection, focuses on the most impactful
predictors without overfitting, providing valuable insights for
strategic pricing and product development.

<br>

## Stepwise Regression Methods

Stepwise regression methods are statistical techniques used to select
the most significant variables in a regression model which involve
adding or removing predictors based on certain criteria in order to
improve the model's performance while avoiding overfitting. Before
proceeding with the stepwise regression methods, let’s generalise the
linear models (full model, model 1, model 2, model 3, model 4, model 5)
first.

### Full Model

```{r}

# Fit a generalized linear model to predict Price using all variables in data_phone
fullmodel <- glm(Price ~ ., data = data_phone)

# Display a summary of the fullmodel
summary(fullmodel)

```

The full model, which is with all the predictors, has been generalised.
The value of Akaike Information Criterion (AIC) is 1999.6. It is hard to
say this is the best as comparison is needed to compute which model is
with the lowest AIC. AIC is a measure used to determine the model's
quality where the goodness of fit and the number of parameters used are
considered. Therefore, lower AIC values indicate a better model.

<br>

### Null Model

```{r}

# Fit a null model (intercept-only model) to predict Price
nullmodel <- glm(Price ~ 1, data = data_phone)

# Display a summary of the null model
summary(nullmodel)

```

The null model, which is with the intercept only, has been generalised.
The value of AIC is 2402.7. This shows that the full model is a better
model for now in terms of value of AIC.

<br>

### Model 1

```{r}

# Convert model1 to a generalized linear model
model_1 <- glm(model1)

# Display a summary of model_1
summary(model_1)

```

Model 1 has been generalised. The value of AIC is 2164.7. This shows
that the full model is the best model for now in terms of value of AIC.

<br>

### Model 2

```{r}
# Convert model2 to a generalized linear model
model_2 <- glm(model2)

# Display a summary of model_2
summary(model_2)

```

Model 2 has been generalised. The value of AIC is 2331.7. This shows
that the full model still is the best for now in terms of value of AIC.

<br>

### Model 3

```{r}

# Convert model3 to a generalized linear model
model_3 <- glm(model3)

# Display a summary of model_3
summary(model_3)

```

Model 3 has been generalised. The value of AIC is 2111.5. This shows
that the full model still is the best for now in terms of value of AIC.

<br>

### Model 4

```{r}

# Convert model4 to a generalized linear model
model_4 <- glm(model4)

# Display a summary of model_4
summary(model_4)

```

Model 4 has been generalised. The value of AIC is 2164.1. This shows
that the full model still is the best for now in terms of value of AIC.

<br>

### Model 5

```{r}

# Convert model5 to a generalized linear model
model_5 <- glm(model5)

# Display a summary of model_5
summary(model_5)

```

Model 5 has been generalised. The value of AIC is 1996.8. This shows
that the model is the best for now in terms of value of AIC.

<br>

### Perform stepwise regression model

This method combines forward and backward stepwise regression. It begins
with an empty model (null model) and adds predictors one by one, similar
to forward stepwise regression. After adding a predictor, the model
checks if any of the included predictors can be removed without
significantly affecting the model fit. This iterative process of adding
and removing predictors continues until no further improvements can be
made.

```{r}

# Perform stepwise model selection from nullmodel to fullmodel in both directions
model.step <- step(nullmodel, scope=list(lower = nullmodel,
                                         upper = fullmodel,
                                         direction = "both"))

# Display a summary of the selected model
summary(model.step)

```

**Analysis:**

The stepwise regression model has performed. The value of AIC is 1996.3.
By this method, the predictors advised to consider are RAM, CPU_core,
PPI, Thickness, InternalMem, CPU_freq, Battery, ScreenSize, FrontCam.

<br>

### Perform Forward Stepwise

This method begins with an empty model (null model) and adds predictors
one by one. At each step, a predictor is added based on criteria such as
AIC, BIC, or p-value to improve model fit. This process of adding
predictors continues iterate until no further improvements can be made.

```{r}

# Perform forward stepwise model selection from nullmodel to fullmodel
forward.model <- step(nullmodel, scope=list(lower=nullmodel,
                                            upper=fullmodel,
                                            direction = "forward"))

# Display a summary of the selected model
summary(forward.model)

```

**Analysis:**

The forward stepwise performed. The value of AIC is 1996.3. By this
method, the predictors advised to consider are RAM, CPU_core, PPI,
Thickness, InternalMem, CPU_freq, Battery, ScreenSize, FrontCam.
Surprisingly, the value of AIC and predictors to take is the same as the
stepwise regression model.

<br>

### Perform Backward Stepwise

This method starts with the full model (full model) and removes the
least important predictors one by one. At each step, a predictor is
removed based on its p-value to improve model fit. This process of
removing predictors continues iterate until no further improvements can
be made.

```{r}

# Perform backward stepwise model selection from fullmodel
backward.model <- step(fullmodel, scope=list(fullmodel, direction = "backward"))

# Display a summary of the selected model
summary(backward.model)

```

**Analysis:**

The backward stepwise performed. The value of AIC is 1996.3. By this
method, the predictors advised to consider are RAM, CPU_core, PPI,
Thickness, InternalMem, CPU_freq, Battery, ScreenSize, FrontCam.
Surprisingly, the value of AIC and predictors to take is the same as
both stepwise methods above.

<br>

### Model 6

After performing the stepwise models above, they concluded to have the
same model. Therefore, model6 is defined with the predictors: RAM,
CPU_core, PPI, Thickness, InternalMem, CPU_freq, Battery, ScreenSize,
FrontCam.

```{r}

# Fit a linear regression model to predict Price according to the results of the stepwise regression model approach
model6 <- lm(Price ~ ScreenSize + PPI + CPU_core + CPU_freq + 
    InternalMem + RAM + FrontCam + Battery + Thickness, data = data_phone)

# Display a summary of model6
summary(model6)

```

**Model Performance:**

-   **Residual standard error:** 172.9 on 141 degrees of freedom
    -   Indicates variability around the fitted values, with a
        reasonably low error suggesting good model fit.
-   **Multiple R-squared:** 0.9398
    -   About 93.98% of the variability in phone prices is explained by
        this model, which is very high, showing excellent explanatory
        power.
-   **Adjusted R-squared:** 0.936
    -   Adjusts the R-squared for the number of predictors, still
        indicating a strong fit.
-   **F-statistic:** 244.8 on 9 and 141 DF, p-value: \< 2.2e-16
    -   The overall model fit is statistically significant, suggesting
        that the predictors collectively have a significant effect on
        phone prices.

**Significance Summary:**

We can observe the significance of each coefficients from the summary
above:

-   **Significant Positive Predictors:** PPI, CPU Core, CPU Frequency,
    Internal Memory, RAM, Battery
-   **Significant Negative Predictors:** Screen Size, Thickness
-   **Non-significant Predictors:** Front Camera

**Conclusion:**

Model 6 demonstrates a robust fit, explaining about 93.98% of the
variability in phone prices, as indicated by the high R-squared value.
Key features such as PPI, CPU core, CPU frequency, internal memory, RAM,
and battery significantly influence price positively. In contrast,
screen size and thickness have a negative impact on price. The low
residual standard error suggests accurate predictions, and the overall
model is statistically significant, confirming the predictors'
collective effect on phone prices.

<br>

# Calculate Mallows' C$p$

Mallows’ C$p$ statistics act as a criteria to evaluate model fits when
comparing models with different numbers of parameters.

```{r}

# Calculate Mallows' Cp for all the models, rounding to 4 decimal places
mallows_cp <- c(round(ols_mallows_cp(full_model,full_model),4),
                round(ols_mallows_cp(model1,full_model),4),
                round(ols_mallows_cp(model2,full_model),4),
                round(ols_mallows_cp(model3,full_model),4),
                round(ols_mallows_cp(model4,full_model),4),
                round(ols_mallows_cp(model5,full_model),4),
                round(ols_mallows_cp(model6,full_model),4))

# Display the calculated Mallows' Cp values
mallows_cp

```

The Mallows’ C$p$ for all six models are calculated. We can observed
that Model 6 has the lowest Mallows’ C$p$ value of 8.6945.

<br>

# Model Selection

```{r}

# Calculate R-squared values for all the models, rounding to 4 decimal places
r <- c(round(summary(full_model)$r.squared,4),
       round(summary(model1)$r.squared,4),
       round(summary(model2)$r.squared,4),
       round(summary(model3)$r.squared,4),
       round(summary(model4)$r.squared,4),
       round(summary(model5)$r.squared,4),
       round(summary(model6)$r.squared,4))

# Calculate Adjusted R-squared values for all the models, rounding to 4 decimal places
adj.r <- c(round(summary(full_model)$adj.r.squared,4),
           round(summary(model1)$adj.r.squared,4),
           round(summary(model2)$adj.r.squared,4),
           round(summary(model3)$adj.r.squared,4),
           round(summary(model4)$adj.r.squared,4),
           round(summary(model5)$adj.r.squared,4),
           round(summary(model6)$adj.r.squared,4))

# Define model names for the summary
mod.names <- c("Full Model", "Model 1", "Model 2", "Model 3", "Model 4", "Model 5", "Model 6")

# Create a data frame summarizing model names, R-squared, Adjusted R-squared, and Mallows' Cp values
summary_r <- data.frame(
  Model = mod.names,
  R_Squared = r,
  Adjusted_R_Squared = adj.r,
  Mallows_Cp = mallows_cp
)

# Create a list of models to be compared
models <- list(full_model, model1, model2, model3, model4, model5, model6)

# Calculate AIC values for the candidate models
aic <- aictab(cand.set = models, modnames = mod.names)

# Merge the summary data frame with the AIC results by model names
slc.model <- merge(summary_r, aic, by.x = "Model", by.y = "Modnames")

# Sort the merged data frame by R-squared values in descending order
slc.model <- slc.model[order(-slc.model$R_Squared),]

# Display the sorted model comparison table
slc.model

```

To select the best model, a few criteria should be considered:

1.  **R-Squared:** From the table above, the Full Model, Model 6 and
    Model 5 have a very similar R-Squared value which is 0.9401, 0.9398,
    0.9388 respectively. This indicates that these models are having a
    similar proportion of the variance in the dependent variables.
    Therefore, Full Model and Model 6 are more preferable in terms of
    this criterion

2.  **Adjusted R-Squared:** Model 6 has the highest Adjusted R-Squared
    (0.9360). Although Full Model (0.9354) and Model 5 (0.9354) just
    slightly lower compared to Model 6 in terms of the Adjusted
    R-Squared. This shows that Model 6 provides a slightly better fit
    when considering the number of predictors. Therefore, Model 6 is
    preferred in terms of this criterion.

3.  **Mallows C**$p$: Model 6 has the lowest Mallows C$p$ (8.6945) as
    compared to Full Model (12.0000) and Model 5 (9.0228). A lower C$p$
    value and closer to the number of predictors (K) will indicates a
    better model. In terms of this criterion, Model 5 is preferred.

4.  **Number of Predictors (K):** Full Model uses 13 predictors, Model 6
    uses 11 predictors, while Model 5 uses 10 predictors. Model 6 and
    Model 5 will be considerate as fewer predictors will be preferable
    if the model fit is similar because it reduces the complexity and
    risk of over fitting.

5.  **AICc (Akaike Information Criterion corrected):** A lower value of
    AICc indicate a better model as AICc is a measure of the relative
    quality of a model. This shows that Model 6 is the most preferable
    model in terms of this criterion as Model 6's AICc is the lowest
    among the models which is 1998.216. But Model 5 still can be under
    considerate as the Model 5's AICc (1998.364) is just slightly higher
    than Model 6.

**Conclusion**

**Based on the criteria above, Model 6 can be concluded as the best
model to use**, given the slight differences in R-Squared and Adjusted
R-Squared, and considering that Model 6 has a lower Mallows C$p$, uses
fewer predictors, and has the lowest AICc. Through these, Model 6
provides the most comparable fit among the models but with less
complexity and better overall performance as indicated by the lower
Mallows's C$p$ and AICc values.

<br>

## Best Model

After the selection of models, the best model is model 6.

```{r}

# Assign model6 as the best model
best_model <- model6

```

<br>

# Standardized Residuals and Studentized Residuals

```{r}

# Calculate standard residuals from the best model
standardresidual <- rstandard(best_model)
dfstandardresidual <- data.frame(standardresidual)

# Calculate studentized residuals from the best model
studentizedresidual <- studres(best_model)
dfstudentizedresidual <- data.frame(studentizedresidual)

# Add an index column for plotting
dfstandardresidual$x <- seq(1:nrow(dfstandardresidual))
dfstudentizedresidual$x <- seq(1:nrow(dfstudentizedresidual))

# Plot a histogram of standard residuals
plot1 <- ggplot(dfstandardresidual, aes(x = standardresidual)) + 
  geom_histogram(binwidth = 0.5, fill = "coral4") +
  ggtitle("Histogram of Standard Residuals")

# Plot a histogram of studentized residuals
plot2 <- ggplot(dfstudentizedresidual, aes(x = studentizedresidual)) + 
  geom_histogram(binwidth = 0.5, fill = "darkslateblue") +
  ggtitle("Histogram of Studentized Residuals")

# Scatter plot of standard residuals against their index
plot3 <- ggplot(dfstandardresidual, aes(x = x, y = standardresidual)) + 
  geom_point(color = "cornflowerblue") +
  ggtitle("Standard Residuals vs Index")

# Scatter plot of studentized residuals against their index
plot4 <- ggplot(dfstudentizedresidual, aes(x = x, y = studentizedresidual)) + 
  geom_point(color = "brown3") +
  ggtitle("Studentized Residuals vs Index")

# Arrange the plots in a 2x2 grid
grid.arrange(plot1, plot2, plot3, plot4, nrow = 2, ncol = 2)

```

**Interpretation:**

Standardized residuals standardize the residuals by dividing each
residual by its estimated standard deviation that is normally
distributed and adjusting its standard deviation to 1. Standardized
residuals close to 0 indicate that the observed values are close to what
is predicted by the model, while values far from 0 indicate potential
outliers or points where the model may not fit well.

While studentized residuals standardize the residual by dividing each
residual by an estimate of its standard deviation that takes into
account the influence (leverage) of each observation on the model fit.

They are typically used for assessing the overall fit of the model and
identifying outliers.

It may be inferred that the **residuals are normally distributed in
general** from the histograms of the studentized and standardised
residuals, which exhibit normal distribution. This is a positive
indicator as it indicates that one of the **fundamental requirements of
linear regression (normally distributed residuals) has been met**. Model
6 appears to be accurately representing the relationship between the
predictors and the response variable, based on the residuals' normality.

However, some residuals on the right-hand side of the histogram seem to
be the outliers as they separate distinctly from the other values. The
presence of outliers is further supported by the scatterplots of the
standardised and studentized residuals, which reveal that most dots fall
between the intervals of -2 and 2, with only 4 dots falling outside of
it.

<br>

# Diagnostic Plots

```{r}

# Set up a 2x2 plotting area and create diagnostic plots for the best_model
par(mfrow = c(2, 2))
plot(best_model)

```

Four diagnostic plots are generated for model 6 to assess the quality
and assumptions of the regression model.

**Residuals vs Fitted:**

-   This graph checks the linearity assumption and identifies non-linear
    patterns. There appears to be a **slight trend in the residuals**,
    suggesting potential non-linearity or that some predictor variables
    might be missing from the model.

**Normal Q-Q:**

-   This graph checks if the residuals are normally distributed. In the
    plot, the points mostly lie along the 45-degree line, suggesting the
    residuals are **approximately normally distributed**, although there
    are **some deviations at the tails**.

**Scale-Location (Spread-Location):**

-   This graph checks the homoscedasticity assumption, that is the
    constant variance of residuals. In the plot, the **residuals are
    spread fairly constant across the fitted values**, the red line is
    also relatively horizontal, though there is some indication of
    increasing variance with higher fitted values.

**Residuals vs Leverage:**

-   This graph identifies influential data points that have a high
    leverage or high residual. In the plot, **most points lie within
    Cook's distance lines**, but there are some potentially influential
    points, but they do not have an excessive influence on the model,
    none seem overly problematic.

<br>

# Confidence level

The 95% confidence intervals for each coefficient in model 6 is
calculated.

```{r}

# Calculate confidence intervals for the coefficients of the best_model
confint(best_model)

```

The **intercept term is statistically significant**, suggesting that the
baseline price of a mobile phone (when all other variables are zero)
falls within this range. **For the other variables excluding front
camera, the absence of zero within these intervals indicates the
statistical significance of the corresponding coefficients.** The
coefficient of screen size and thickness falls within the negative
range, indicating these two variables are negatively correlated to the
mobile phone price. On the other hand, the coefficient of the remaining
variables falls within the positive range, indicating the variables are
positively correlated to the mobile phone price. **As the confidence
interval of the front camera ranges from -2.14 to 16.90, which includes
zero, it suggests that the effect of the front camera on price is not
statistically significant at the 95% confidence level.**

<br>

# ANOVA

```{r}

# Perform ANOVA analysis on the best_model to assess the significance of predictors
anova(best_model)

```

Analysis of variance (ANOVA) is performed on model 6 to assess the
significance of each predictor in the regression model. **Overall, the
variables in the model are statistically significant predictors of
mobile phone price, with the exception of the front camera, which is not
significant**. However, the significance of the variables can be further
interpreted by assessing the Pr(\>F) values. Pr(\>F) values less than
0.05 are considered statistically significant at the 5% significance
level. ScreenSize, PPI, CPU_core, InternalMem, RAM, Thickness, CPU_freq
and Battery all have Pr(\>F) values less than 0.05, indicating they are
highly significant predictors. On the other hand, **FrontCam has a
Pr(\>F) value approximately 0.15, indicating that the front camera does
not significantly affect phone pricing at the 5% significance level.**

<br>

# Conclusion

**Topic Overview and Data Description**

The primary focus of this study is to explore the mobile phone market,
particularly how various features influence the pricing of mobile
phones. We utilised a comprehensive dataset from Kaggle, which includes
diverse specifications such as weight, thickness, battery capacity,
screen resolution, pixels per inch (PPI), camera features, CPU
specifications, internal memory, and RAM. These variables form the
backbone of our analysis, helping us understand which factors consumers
value most when it comes to mobile phone pricing.

**Model Setup and Analysis**

To effectively address the project's objectives, multiple regression
models were designed to identify the variables that most significantly
impact mobile phone pricing. In total, we constructed six distinct
models, each incorporating various combinations of the aforementioned
features. These models were rigorously analysed to discern how well they
explained the variability in mobile phone prices.

**Model Selection Key Points and Best Model Determination**

The selection of the best model was based on several statistical
criteria:

-   **R-Squared and Adjusted R-Squared:** These metrics showed that
    Models 5 and 6 closely followed the Full Model in terms of
    explanatory power, indicating robust model performance.
-   **Mallows' Cp:** Among the models, Model 6 demonstrated a lower Cp
    value, suggesting it has a good balance between accuracy and
    simplicity.
-   **Number of Predictors and AICc:** Model 6, with fewer predictors
    and the lowest AICc, provided an optimal balance, reducing
    complexity while maintaining a high level of explanatory power.

Based on these criteria, Model 6 emerged as the best model. It
effectively captured the relationship between mobile phone features and
pricing with sufficient complexity to avoid overfitting.

**Significant Predictors and Their Implications**

The best model highlighted several significant predictors of mobile
phone pricing as they directly relate to the performance and user
experience of a mobile phone. According to Maesya et al. (2023), RAM,
number of CPU cores, CPU frequency, PPI, internal memory and battery
have significantly positive impacts on the price of mobile phones, which
also has been evident by several other studies (Listianingrum et al.,
2021; Ahmad et al., 2019). The positive relationship between these
variables and price indicates that consumers are willing to pay more for
higher performance and better display quality. Moreover, it is also
revealed that screen size and thickness significantly negatively impacts
mobile prices. On the other hand, studies have also indicated that
although camera quality can affect consumers' decisions, the front
camera in particular does not have as much of an impact on the final
price as other features do (Maesya et al., 2023; Listianingrum et al.,
2021).

**Implications for Mobile Phone Companies**

The findings from this study provide actionable insights for mobile
phone companies. By understanding the features that significantly affect
pricing, companies can strategically design their products to align with
consumer preferences. For instance, investing in advanced display
technology and higher memory capacities can justify higher price points
and cater to consumer demand for more powerful devices. Moreover, the
preference for sleeker designs, as indicated by the negative correlation
with thickness, suggests that slimmer phones could be marketed as
premium offerings.

In conclusion, this analysis not only aids in setting competitive
pricing strategies but also guides product development by highlighting
the features that are most valued by consumers in different market
segments. By tailoring products according to these insights, mobile
phone companies can better meet consumer expectations and enhance their
market position and also attain a goal of maximising profit.
